### 2011-03-08 projectWriteup/paper.tex
Added the tex files for the writeup

\documentclass[12pt]{article}
\usepackage{e-jc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{url}
\long\def\symbolfootnote[#1]#2{\begingroup%
\def\thefootnote{\fnsymbol{footnote}}\footnote[#1]{#2}\endgroup}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

\title{A Balanced Agent for Capture The Flag Pac-Man}

\author{
Alexander L. Churchill\\
\small \texttt{achur@stanford.edu}\\
\and
Emilio Lopez\\
\small \texttt{elopez1@stanford.edu}\\
\and
Rafael Witten\\
\small \texttt{rwitten@stanford.edu}
}

\date{Mar. 8, 2011}

\begin{document}
\maketitle
\section{Introduction}
Building a balanced Pac Man: the work of champions.

% This is the Bibliography
%%%%%%%%%%%%%%%

\begin{thebibliography}{99}

\bibitem{carlisle} Carlisle, A., Dozier, G. (2001). ``An Off-The-Shelf PSO''.
  {\it Proceedings of the Particle Swarm Optimization Workshop}. pp. 1-6.

\end{thebibliography}

\end{document}

### 2011-03-08 projectWriteup/paper.tex
Added the introduction to the paper
Note that when using pdflatex to compile paper.tex, to
get citations working, sometimes you have to compile like
2 or 3 times (since the bibliography is at the end and
LaTeX compiles unidirectionally).

@@
 \section{Introduction}
-Building a balanced Pac Man: the work of champions.
+A popular and relevant field in artificial intelligence is noisy gameplay
+\cite{miik}.  Noisy readouts, opposing agents, and limited calculation
+time, mean that noisy games are open to a wide variety of AI techniques.
+One particularly relevant example of this field is Capture the Flag (CTF)
+Pac-Man, in which a team of independent agents tries to simultaneously
+protect food on their side of a Pac-Man board while eating the food on
+their opponents' side.  In this paper, we discuss our implementation of a
+balanced agent to play CTF Pac-Man.
+\\ \\
+In our balanced agent, we observed that there are three main branches of
+strategy in CTF Pac-Man: attacking, holding the line, and defending.  The
+first attempts to eat opposing food, the second attempts to block opposing
+agents from entering our side, and the third attempts to capture opposing
+agents and prevent them from eating our food once they cross over.  We
+built individual modules for each one of these strategies to recommend
+moves.  As in many AI agents, the recommendations of these modules and the
+global decision which module to apply use a combination of minimax and
+expectimax, where we look several moves ahead, analyze the strength of our
+position, and act accordingly.
+\\ \\
+Our differentiator and the primary focus of our work was on more advanced
+ways to model opponents and determine the strength of a given game state,
+as well as techniques to optimize the weights used to combine those
+parameters into relevant state values.  For inference of opponent agent
+positions, using prior knowledge and the noisy readings we could observe,
+we used more than just sensor data, and incorporated a basic opponent
+model.  Our various agents incorporated a wide variety of heuristics,
+weighted to recommend moves.  We used a technique called Particle Swarm
+Optimization (PSO) to find a string set of weights.  PSO tends to perform
+well in functions like ours that are difficult to evaluate accurately and
+impossible to analyze from a theoretical perspective \cite{carlisle}.
+Furthermore, we observed that the best weightings varied between different
+layouts.  Therefore, we trained weights for many different boards.  When
+presented with a new board, we clustered it with similar boards (based on
+a number of features of the layout) for which
+we had trained values and used an average of those values.  The result is
+an agent that has learned how to play well on a variety of different
+layouts with a variety of different strategies, and combines that
+knowledge effectively when presented with a new game.
+
+\section{Heuristics}
+\subsection{Offense}
+\subsection{Defense}
+\subsection{Hold the Line}
+
+\section{Inference}
+
+\section{Particle Swarm Optimization}
+\subsection{Algorithm}
+\subsection{Theoretical Justification}
+\subsection{Performance and Results}
+
+\section{$k$-means Clustering for Layouts}
+To solve this problem of disparate weights selected by PSO for different
+layouts, given a layout, we attempted to determine similar layouts for
+which we had already computed training data.  To this end, we used
+$k$-means cluatering.
+\subsection{Methodology}
+\subsection{Performance and Results}
+
+\section{Overall Results}
+
+\section{Discussion}
 
@@
 
+\bibitem{miik} Miikkulainen, R. (2006) ``Creating Intelligent
+  Agents in Games''.  {\it The Bridge}.  National Academy of Engineering.
+
 \end{thebibliography}

### 2011-03-08 projectWriteup/paper.tex
Edited inference section

@@
 \section{Inference}
-
+For inference of opponent agent positions, we update prior probabilities based not only on our sensor readings, but also based on assumptions in our opponent model, which assumes that the opponent is at all times more likely to be moving towards our food and, therefore, places higher probabilities on positions that get them closer.
+Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever one moved before our agent who's analyzing his sensor readings).
+We're also very careful in our inference module about cases where we eat an opponent, to update the probabilities to reflect that they're starting over at their initial position
 \section{Particle Swarm Optimization}

### 2011-03-09 projectWriteup/paper.tex
Addition to papers to flesh out sections

--- 2011-03-08 projectWriteup/paper.tex
@@
 \usepackage{amsthm}
+\usepackage{algorithmic}
+
 \usepackage{graphicx}
@@
 
-\title{A Balanced Agent for Capture The Flag Pac-Man}
+\title{An Optimized Agent for Capture The Flag Pac-Man}
 
@@
 moves.  As in many AI agents, the recommendations of these modules and the
-global decision which module to apply use a combination of minimax and
+global decision of which module to apply use a combination of minimax and
 expectimax, where we look several moves ahead, analyze the strength of our
@@
 Our differentiator and the primary focus of our work was on more advanced
-ways to model opponents and determine the strength of a given game state,
+ways to model opponents and determine the value of a given game state,
 as well as techniques to optimize the weights used to combine those
@@
 \section{Heuristics}
+We thought much more about our choice of heuristics than about their weights, relying instead on automated techniques to choose optimal parameters.
+Our choice of heuristics was primarily driven by attempting to think about things in ways similar to humans; in each ``mode" we evaluated the position using heuristics relevant to examining the board from the perspective of the human strategy.
+
+Hence, we wrote a heuristic function that looked at a board and classified each of the agents, theirs and ours, as being in one of those three states.
+To evaluate a position we took a weighted sum of how the three heuristics thought we were doing; thus our heuristic was considering a weighting of how well our defenders were protecting our dots, our attackers were threatening their dots and our hold the line agents were preventing them from crossing onto our side.
 \subsection{Offense}
 \subsection{Defense}
+The defensive heuristics that we found most helpful were putting emphasis on staying close to our enemies, getting them into one exit scenarios and ensuring that for any piece of food we were closer than our opponents.
+A key limitation that we had was that losing sight of attacking enemies could be very dangerous because lack of information is very helpful to attackers.
+However, because we were able to deduce an exact location any time food went missing, any agent that was doing serious harm was inherently easy to track.
 \subsection{Hold the Line}
+Playing defense against agents who had not crossed onto our side was a very different problem than playing it against agents who had, mostly because trying to eat them was no longer a strong strategy.
+Hence we hit upon the idea of separating that type of play into a ``Hold The Line" heuristic.
+For the purposes of holding the line, our agents would ``match up'' against usually one but sometimes more, if we had some agents attacking, opposing agents and mirror their moves, trying to stay closer to all of the squares on the border than the opponents that that agent was ``covering''.
+With good inference, as is possible in a 6 agent game, it could become very hard for any opposing agents to cross the border.
 
 \section{Inference}
+For inference of opponent agent positions, we update prior probabilities based not only on our sensor readings, but also based on assumptions in our opponent model, which assumes that the opponent is at all times more likely to be moving towards our food and, therefore, places higher probabilities on positions that get them closer.
+Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever agent moved before our agent who' is currently analyzing his sensor readings).
+We are also careful in our inference module about cases where we eat an opponent, to update the probabilities to reflect that they are starting over at their initial position.
 
 \section{Particle Swarm Optimization}
+The fitness function that we were trying to maximize is, of course, how well an agent plays.
+However, evaluating the performance of a strategy is tricky because it requires playing many games to determine a win percentage against some training set of agents and evaluating some measure of fitness.
+Evaluating a win percentage is quite noisy and playing a single pacman game is computationally very expensive (as much as 50 minutes, although for training purposes we cutdown thinking time to make games around 5 minutes long).
+Hence, when evaluating our agents we got very noisy results.
+
+Part of the appeal of Particle Swarm Optimization (PSO) is that it has in practice been shown to be fairly robust against noise in evaluating an objective function.
+PSO was proposed in 1995 by \cite{originalref} for optimizing functions that are continuous but have no other useful structure.
+The appeal of PSO over a monte carlo stochastic optimization scheme such as \cite{montecarlo} is that we have a strong suspicion that our true objective function is locally pretty smooth, which fits nicely with local search based methods like PSO.
+Additionally using more particles helps us avoid local minima to which genetic algorithms are susceptible as suggested by \cite{geneticalgorithm}.
+However, gradient descent is not an option because we cannot compute a first derivative and empirical gradient descent would be noisy because we cannot accurately compute the function at any one point so our empirical gradients would be very inaccurate.
+
 \subsection{Algorithm}
-\subsection{Theoretical Justification}
+We assume that we're given a number of particles to use $N$ and a number of steps to iterate for $k$.
+We assume that we can sample uniformly from the feasible state space, $C$, which is chosen to be a rectangle in $\Bbb R^n$, and $C_v$ which is the set of original feasible speeds.
+The algorithm that we used is a variant of PSO that we created specifically to cut down on expensive function evaluations and an adaption of previous variants of PSO such as \cite{carlisle}.
+\\
+
+{ \bf Binary PSO}
+\begin{algorithmic}
+\FOR { each particle $i$ in $1,..., N$} 
+  \STATE Draw $x_i \sim C$.
+  \STATE Set $p_i = x_i$.   $p_i$ is the particle's optimal point.
+  \STATE Draw $v_i \sim C_v$.
+\ENDFOR
+\STATE Choose $p$ to be the $\text{winner}_i (p)$, so $p$ are the swarm's best point and value so far.
+
+\FOR {iterations $j$ in $1, ..., k$}
+  \FOR{ each particle $i$ in $1, ..., N$}
+     \STATE Pick random numbers $r_p, r_g \sim U(0,1)$.
+     \STATE Set $v_i = \omega v_i + \omega_p r_p (p_i - x_i) + \omega_g r_g (p -x_i)$.
+     \STATE Set $x_i = x_i + v_i$.
+     \IF {$x_i >_{agent} p_i$}
+       \STATE Set $p_i=x_i$.
+       \IF{$p_i >_{agent} p$}
+         \STATE Set $p = p_i$.
+       \ENDIF
+     \ENDIF
+  \ENDFOR
+\ENDFOR
+
+The parts of the algorithm that have not be fleshed out are the comparisons between points.
+The operator $>_{agent}$ means that the agent on the left hand side beat the agent on the right hand side in head to head play in a statistically significant way.
+The ``winner" method means selecting the ``best'' element by single matchup elimination tournament, using the $>_{agent}$ operator.
+\end{algorithmic}
+
 \subsection{Performance and Results}
@@
 \section{$k$-means Clustering for Layouts}
-To solve this problem of disparate weights selected by PSO for different
-layouts, given a layout, we attempted to determine similar layouts for
-which we had already computed training data.  To this end, we used
-$k$-means cluatering.
+To solve this problem of disparate weights selected by PSO for different layouts, given a layout, we attempted to determine similar layouts for which we had already computed training data.
+The idea was that using the single ``closest'' layout would be a mistake since each of our weights were computed by PSO and were thus subject to noise; adding independent results therefore seems likely to result in better performance.
+
 \subsection{Methodology}
+We trained 20 different agents on each of the contest layouts.
+Additionally we extracted some features from each board - such as amount of food, size and number of agents.
+Then we used k-means clustering to choose a handful of clusters that capture the data pretty well.
+The choice of k-means clustering was done because it seemed likely that clustering might help as suggested by \cite{textbook} and we consider k-means clustering to be the default for problems without a prior \cite{kmeans}.
+Moreover the the centroid of a set of points is the natural choice for how we would mix a set of heuristics, making k-means seem to match the same prior.
+
+When given a new board, our agents chose the cluster it belongs to and played with the average weights in its cluster.
+
 \subsection{Performance and Results}
-
-\section{Overall Results}
 
@@
 
+\bibitem{montecarlo} Hauskrecht, A., Singliar, T. (2003). ``Monte-Carlo optimizations for resource allocation problems in stochastic network systems".
+
+\bibitem{originalref} Kennedy, J.; Eberhart, R. (1995). ``Particle Swarm Optimization". 
+  {\it Proceedings of IEEE International Conference on Neural Networks. IV.} pp. 1942-1948.
+
+\bibitem{kmeans} MacQueen, J.
+B.
+(1967).
+"Some Methods for classification and Analysis of Multivariate Observations".
+{\it Proceedings of 5th Berkeley Symposium on Mathematical Statistics and Probability.} University of California Press.
+pp.
+281Ð297.
+
 \bibitem{miik} Miikkulainen, R. (2006) ``Creating Intelligent
   Agents in Games''.  {\it The Bridge}.  National Academy of Engineering.
+
+\bibitem{geneticalgorithm} Rocha, M., Neves J.
+(1999) ``Preventing premature convergence to local optima in genetic algorithms via random offspring generation''.
+{\it IEA/AIE '99 Proceedings of the 12th international conference on Industrial and engineering applications of artificial intelligence and expert system}.
+
+\bibitem{textbook} Russell, S., Norvig, P. (2010) ``Artificial Intelligence''. {\it A Modern Approach Third Edition} , Prentice Hall.
 

### 2011-03-09 contest/attackModule.py
Fixin bugs

@@ -4,11 +4,14 @@ import minimaxModule
 from minimaxModule import MinimaxModule
 import random
 import time
+import cellLayout
 
 class AttackModule(agentModule, minimaxModule.MinimaxModuleDelegate):
 
   def chooseAction(self, gameState):
+      print("Agent " + str(self.index) + " choosing an action")
       minimaxMod = MinimaxModule(self)
+      minimaxMod.setImpatience(float(self.heuristicWeights['attackModule_percentImpatience'])/100.0)
       minimaxVals = minimaxMod.getMinimaxValues(gameState, self.index, self.isRed, 0.1)
       bestActions = []
       bestVal = 0
@@ -24,14 +27,16 @@ class AttackModule(agentModule, minimaxModule.MinimaxModuleDelegate):
       return random.choice(bestActions)
 
   def getStateValue(self, gameState):
-      foodDistances = self.distanceToFood(gameState, False) if self.isRed else self.distanceToFood(gameState, True)
+      foodDistances = self.distanceToFood(gameState, not self.isRed)
       nearestFoodVal = self.heuristicWeights['attackModule_nearestFoodCoeff'] * pow(foodDistances[0], self.heuristicWeights['attackModule_nearestFoodPower'])
       totalFoodVal = self.heuristicWeights['attackModule_totalFoodCoeff'] * foodDistances[1]
-      foodCount = self.getFoodCount(gameState, False) if self.isRed else self.getFoodCount(gameState, True)
-      numFoodsVal = self.heuristicWeights['attackModule_foodEatenReward'] * (20 - self.getFoodCount(gameState, False))
+      nearestCapsuleVal = self.heuristicWeights['attackModule_nearestCapsuleCoeff'] * self.nearestCapsule(gameState)
+      foodCount = self.getFoodCount(gameState, not self.isRed)
+      numFoodsVal = self.heuristicWeights['attackModule_foodEatenReward'] * self.getFoodCount(gameState, not self.isRed)
       distanceApartVal = self.heuristicWeights['attackModule_distanceApartReward'] * self.distanceApart(gameState)
       enemyDistanceVal = self.heuristicWeights['attackModule_distanceToEnemies'] * self.distanceToEnemies(gameState)
-      return numFoodsVal - nearestFoodVal - totalFoodVal + distanceApartVal + enemyDistanceVal
+      trappedPenaltyVal = self.heuristicWeights['attackModule_trappedPenaltyCoeff'] *self.trappedPenalty(gameState)
[…]

### 2011-03-09 contest/cellLayout.py

@@ -186,18 +186,18 @@ class CellLayout:
                 else:
                     return (False, [])
             # if we get here, we are in a two-sided pipe
-            neighbor0 = startNode.getPositions()[0]
+            neighbor0 = startNode.getNeighbors()[0]
             if(len(neighbor0.getPositions()) > 1):
                 return (False, []) # here we are in a loop, so it can always loop away
             neighbor0pos = neighbor0.getPositions()[0]
             trapperDist = self.distancer.getDistance(trapperPos, neighbor0pos)
             trappedDist = self.distancer.getDistance(trappedPos, neighbor0pos)
             if(trapperDist < trappedDist):
-                neighbor = startNode.getPositions()[0]
+                neighbor = startNode.getNeighbors()[0]
             else:
-                neighbor = startNode.getPositions()[1]
+                neighbor = startNode.getNeighbors()[1]
             blocked = set([])
-            canTrap = canTrapRec(neighbor, depthToSearch, blocked)
+            canTrap = self.canTrapRec(neighbor, depthToSearch, blocked)
             if(canTrap):
                 blockList = [s for s in blocked]
                 if(endNode in blocked):
@@ -207,7 +207,7 @@ class CellLayout:
             return (False, [])
         for neighbor in startNode.getNeighbors():
             blocked = set([])
-            canTrap = canTrapRec(neighbor, depthToSearch, blocked)
+            canTrap = self.canTrapRec(neighbor, depthToSearch, blocked)
             if(canTrap):
                 blockList = [s for s in blocked]
                 if(endNode in blocked):
@@ -216,7 +216,7 @@ class CellLayout:
     
         
     def canTrapRec(self, startNode, depthToSearch, blockedNodes):
-        if(startNode in exploredNodes):
+        if(startNode in blockedNodes):
             return True
         if(depthToSearch == 0):
             return False

### 2011-03-09 contest/ourAgent.py

@@ -16,6 +16,8 @@ from util import nearestPoint
 import particleSwarmOptimizer
 from particleSwarmOptimizer import ParticleSwarmOptimizable
 import weightsConfig
+import knownWeights
+import cellLayout
 
 def zeros(k):
   zeros = ''
@@ -115,6 +117,11 @@ class ourFactory(AgentFactory):
   def getAgent(self, index):
     curAgent = ourAgent(index, timeForComputing=1)
     curAgent.initialize(self.iModel, self.isRed)
+    curAgent.setWeights(weightsConfig.WeightsMap)
+    if(self.isRed):
+        curAgent.setWeights(weightsConfig.WeightsMap)
+    else:
+        curAgent.setWeights(knownWeights.getWeights("contest02Capture"))
     return curAgent
 
 def createTeam(firstIndex, secondIndex, isRed):
@@ -161,10 +168,11 @@ class ourAgent(CaptureAgent,minimaxModule.MinimaxModuleDelegate, ParticleSwarmOp
       self.enemies = gameState.getRedTeamIndices()
 
     self.inferenceModule.initialize(gameState, self.isRed, self.enemies, self.index)#infModule checks to make sure we don't do this twice
+    self.cellLayout = cellLayout.CellLayout(gameState.data.layout, self.distancer) # pass one of these guys around
     #self.agentModule = module.agentModule(self.friends, self.enemies, self.isRed, self.index,self.inferenceModule)
-    self.holdTheLineModule = holdTheLineModule.holdTheLineModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule,self.distancer)
-    self.defenseModule = defenseModule.defenseModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule,self.distancer)
-    self.attackModule = attackModule.AttackModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule,self.distancer)
+    self.holdTheLineModule = holdTheLineModule.holdTheLineModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
+    self.defenseModule = defenseModule.defenseModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
[…]

### 2011-03-09 projectWriteup/paper.tex

--- 2011-03-08 projectWriteup/paper.tex
@@
 \section{Inference}
-
+For inference of opponent agent positions, we update prior probabilities based not only on our sensor readings, but also based on assumptions in our opponent model, which assumes that the opponent is at all times more likely to be moving towards our food and, therefore, places more probability mass on positions that get them closer.
+Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever one moved before our agent who's analyzing his sensor readings).
+We're also very careful in our inference module about cases where we eat an opponent.
+When this happens, we update the probabilities to reflect that they're starting over at their initial position.
+And when an opponent is visible (i.e.
+in our line of sight), we update our probability mass to show that their position is exactly the one at which we see them.
+Once they're beyond our line of sight, we return to updating prior probabilities the same way we were before.
 \section{Particle Swarm Optimization}

### 2011-03-09 contest/ourAgent.py
Fix another bug

@@ -118,10 +118,6 @@ class ourFactory(AgentFactory):
     curAgent = ourAgent(index, timeForComputing=1)
     curAgent.initialize(self.iModel, self.isRed)
     curAgent.setWeights(weightsConfig.WeightsMap)
-    if(self.isRed):
-        curAgent.setWeights(weightsConfig.WeightsMap)
-    else:
-        curAgent.setWeights(knownWeights.getWeights("contest02Capture"))
     return curAgent
 
 def createTeam(firstIndex, secondIndex, isRed):

### 2011-03-09 contest/ourAgent.py
Adds some stuff

@@ -117,7 +117,6 @@ class ourFactory(AgentFactory):
   def getAgent(self, index):
     curAgent = ourAgent(index, timeForComputing=1)
     curAgent.initialize(self.iModel, self.isRed)
-    curAgent.setWeights(weightsConfig.WeightsMap)
     return curAgent
 
 def createTeam(firstIndex, secondIndex, isRed):
@@ -165,7 +164,9 @@ class ourAgent(CaptureAgent,minimaxModule.MinimaxModuleDelegate, ParticleSwarmOp
 
     self.inferenceModule.initialize(gameState, self.isRed, self.enemies, self.index)#infModule checks to make sure we don't do this twice
     self.cellLayout = cellLayout.CellLayout(gameState.data.layout, self.distancer) # pass one of these guys around
-    #self.agentModule = module.agentModule(self.friends, self.enemies, self.isRed, self.index,self.inferenceModule)
+    
+    curAgent.setWeights(weightsConfig.WeightsMap)
+    
     self.holdTheLineModule = holdTheLineModule.holdTheLineModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
     self.defenseModule = defenseModule.defenseModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
     self.attackModule = attackModule.AttackModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
@@ -278,9 +279,13 @@ class ourAgent(CaptureAgent,minimaxModule.MinimaxModuleDelegate, ParticleSwarmOp
     hltScore = self.holdTheLineModule.evaluateBoard(gameState,hltMatching.keys(), notAttackingEnemies) 
     dScore = self.defenseModule.evaluateBoard(defensiveMatching.values(), self.defenseModule.getOurFood(gameState),attackingEnemies)
     attackScore = self.attackModule.getStateValue(gameState)
+    
+    countAttackModule = 1
+    if self.index not in attackingMatching.keys():
+        countAttackModule=0
     return self.heuristicWeights['ourAgent_hltWeight'] * hltScore \
       +self.heuristicWeights['ourAgent_dWeight']*dScore\
-      +self.heuristicWeights['ourAgent_attackWeight']*attackScore
[…]

### 2011-03-09 contest/weightsConfig.py

@@ -17,10 +17,10 @@ WeightsMap = { \
                 'attackModule_nearestFoodPower' : 1, \
                 'attackModule_nearestFoodCoeff' : 20,  \
                 'attackModule_nearestCapsuleCoeff' : 1,  \
-                'attackModule_totalFoodCoeff'      : 1,  \
+                'attackModule_totalFoodCoeff'      : 2,  \
                 'attackModule_distanceApartReward' : 2,  \
-                'attackModule_distanceToEnemies'   : 1,  \
-                'attackModule_trappedPenaltyCoeff'   : 10,  \
+                'attackModule_distanceToEnemies'   : 10,  \
+                'attackModule_trappedPenaltyCoeff'   : 15,  \
                 'attackModule_percentImpatience'    : 10, \
 
                 'defenseModule_maxMinOrZero' : -10, \
@@ -76,7 +76,7 @@ WeightsRangeMap = { \
                     'ourAgent_theyCanBeAttackingThreshold' : (0,20), \
 
                     'hltAgent_ourAverageDistanceToSquares' : (-10,5), \
-                    'hltAgent_averageInactivity' : (-10,5), \
+                    'hltAgent_averageInactivity' : (-15,10), \
                     'hltAgent_opponentMax' : (-10,5), \
                     'hltAgent_secondMax' : (-10,5), \
                     'hltAgent_zerosecondMax' : (-10,5), \

### 2011-03-09 projectWriteup/paper.tex
some revisions to writeup

--- 2011-03-09 projectWriteup/paper.tex
@@
 \cite{miik}.  Noisy readouts, opposing agents, and limited calculation
-time, mean that noisy games are open to a wide variety of AI techniques.
+time mean that noisy games are open to a wide variety of AI techniques.
 One particularly relevant example of this field is Capture the Flag (CTF)
@@
 We thought much more about our choice of heuristics than about their weights, relying instead on automated techniques to choose optimal parameters.
-Our choice of heuristics was primarily driven by attempting to think about things in ways similar to humans; in each ``mode" we evaluated the position using heuristics relevant to examining the board from the perspective of the human strategy.
+Our choice of heuristics was primarily driven by attempting to think about things in ways similar to humans; in each "mode" - offense, defense, and hold the line - we evaluated the positions using heuristics relevant to examining the board from the perspective of the human strategy.
 
@@
 \subsection{Defense}
-The defensive heuristics that we found most helpful were putting emphasis on staying close to our enemies, getting them into one exit scenarios and ensuring that for any piece of food we were closer than our opponents.
+The defensive heuristics that we found most helpful were putting emphasis on staying close to our enemies, getting them into exit scenarios and ensuring that for any piece of food we were closer than our opponents.
 A key limitation that we had was that losing sight of attacking enemies could be very dangerous because lack of information is very helpful to attackers.
@@
 For inference of opponent agent positions, we update prior probabilities based not only on our sensor readings, but also based on assumptions in our opponent model, which assumes that the opponent is at all times more likely to be moving towards our food and, therefore, places higher probabilities on positions that get them closer.
-Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever agent moved before our agent who' is currently analyzing his sensor readings).
-We are also careful in our inference module about cases where we eat an opponent, to update the probabilities to reflect that they are starting over at their initial position.
-
+Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever agent moved before our agent who is currently analyzing his sensor readings).
+We are also careful in our inference module about cases where we eat an opponent.
+When this happens, we update the probabilities to reflect that they're starting over at their initial position.
+And when an opponent is visible (i.e.
+in our line of sight), we update our probability mass to show that their position is exactly the one at which we see them.
+Once they're beyond our line of sight, we return to updating prior probabilities the same way we were before.
 \section{Particle Swarm Optimization}

### 2011-03-09 projectWriteup/paper.tex
Fixed some final bugs and finished paper

--- 2011-03-09 projectWriteup/paper.tex
@@
 A popular and relevant field in artificial intelligence is noisy gameplay
-\cite{miik}.  Noisy readouts, opposing agents, and limited calculation
-time, mean that noisy games are open to a wide variety of AI techniques.
-One particularly relevant example of this field is Capture the Flag (CTF)
-Pac-Man, in which a team of independent agents tries to simultaneously
-protect food on their side of a Pac-Man board while eating the food on
-their opponents' side.  In this paper, we discuss our implementation of a
-balanced agent to play CTF Pac-Man.
-\\ \\
+\cite{miik}.  One fun example of this field is Capture the Flag (CTF)
+Pac-Man.  In this paper, we discuss our implementation of an optimized, flexible agent to play CTF Pac-Man.
+
 In our balanced agent, we observed that there are three main branches of
@@
 global decision of which module to apply use a combination of minimax and
-expectimax, where we look several moves ahead, analyze the strength of our
-position, and act accordingly.
-\\ \\
+expectimax.
+
 Our differentiator and the primary focus of our work was on more advanced
@@
 as well as techniques to optimize the weights used to combine those
-parameters into relevant state values.  For inference of opponent agent
-positions, using prior knowledge and the noisy readings we could observe,
-we used more than just sensor data, and incorporated a basic opponent
-model.  Our various agents incorporated a wide variety of heuristics,
+parameters into relevant state values.
+We used opponent modeling and clever observations in addition to our noisy readouts to infer our opponents' positions.
+Our various agents incorporated a wide variety of heuristics,
 weighted to recommend moves.  We used a technique called Particle Swarm
-Optimization (PSO) to find a string set of weights.  PSO tends to perform
-well in functions like ours that are difficult to evaluate accurately and
+Optimization (PSO) to find a strong set of weights.  PSO tends to perform
+well in functions like ours that are both difficult to evaluate accurately and
 impossible to analyze from a theoretical perspective \cite{carlisle}.
-Furthermore, we observed that the best weightings varied between different
-layouts.  Therefore, we trained weights for many different boards.  When
-presented with a new board, we clustered it with similar boards (based on
-a number of features of the layout) for which
-we had trained values and used an average of those values.  The result is
-an agent that has learned how to play well on a variety of different
-layouts with a variety of different strategies, and combines that
-knowledge effectively when presented with a new game.
+To integrate the specific results of PSO to new layouts, we clustered a layout at gametime with other layouts for which we had pre-computed PSO values.
+
+\section{Inference}
+The first problem we had to solve was that of determining where opposing agents were: the noisy readings from the game state left much to be desired.
+For inference of opponent agent positions, we update prior probabilities based not only on our sensor readings, but also based on assumptions in our opponent model, which assumes that the opponent is at all times more likely to be moving towards our food and, therefore, places higher probabilities on positions that get them closer.
+Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever agent moved before our agent who is currently analyzing its sensor readings).
+For obvious reasons, our inference module also handles the two cases in which we know an opponents' location: when we eat them, their probability mass goes back to their start position, and once they are in ``line of sight'' we update their probability distribution accordingly.
 
@@
 \subsection{Offense}
+Playing offense used a number of heuristics designed to reward agents that could capture food maximally on each attack run.
+We found that the most important heuristics were the number of food on the board, our distance to the nearest food, and our total distance to food items.
+We also included heuristics taking into account how close we were to other agents, both opposing ghosts and teammates.
+Finally, we imposed a heuristic penalty for entering cells of the board that were trapped by opposing agents.
+
 \subsection{Defense}
-The defensive heuristics that we found most helpful were putting emphasis on staying close to our enemies, getting them into one exit scenarios and ensuring that for any piece of food we were closer than our opponents.
-A key limitation that we had was that losing sight of attacking enemies could be very dangerous because lack of information is very helpful to attackers.
+The defensive heuristics that we found most helpful were staying close to our enemies, getting them into single-exit (trapped) scenarios and ensuring that for any piece of food we were closer than our opponents.
+A key limitation that we had was that losing sight of attacking enemies could be very dangerous because mutual lack of information is very helpful to attackers.
 However, because we were able to deduce an exact location any time food went missing, any agent that was doing serious harm was inherently easy to track.
@@
 Hence we hit upon the idea of separating that type of play into a ``Hold The Line" heuristic.
-For the purposes of holding the line, our agents would ``match up'' against usually one but sometimes more, if we had some agents attacking, opposing agents and mirror their moves, trying to stay closer to all of the squares on the border than the opponents that that agent was ``covering''.
+For the purposes of holding the line, our agents would ``match up'' against usually one but sometimes more opposing agents depending on whether we had some agents attacking.
+Our agents mirror their moves, trying to stay closer to all of the squares on the border than the opponents that that agent was ``covering''.
 With good inference, as is possible in a 6 agent game, it could become very hard for any opposing agents to cross the border.
-
-\section{Inference}
-For inference of opponent agent positions, we update prior probabilities based not only on our sensor readings, but also based on assumptions in our opponent model, which assumes that the opponent is at all times more likely to be moving towards our food and, therefore, places higher probabilities on positions that get them closer.
-Additionally, our inference module analyzes our food grid and, whenever one of our pieces of food gets eaten, updates the probabilities of the enemy agent that ate it (whichever agent moved before our agent who' is currently analyzing his sensor readings).
-We are also careful in our inference module about cases where we eat an opponent, to update the probabilities to reflect that they are starting over at their initial position.
 
@@
 
-Part of the appeal of Particle Swarm Optimization (PSO) is that it has in practice been shown to be fairly robust against noise in evaluating an objective function.
+Part of the appeal of Particle Swarm Optimization (PSO) is that it has in practice been shown to be fairly robust against noise in evaluating an objective function \cite{pars}.
 PSO was proposed in 1995 by \cite{originalref} for optimizing functions that are continuous but have no other useful structure.
-The appeal of PSO over a monte carlo stochastic optimization scheme such as \cite{montecarlo} is that we have a strong suspicion that our true objective function is locally pretty smooth, which fits nicely with local search based methods like PSO.
+The appeal of PSO over a Monte Carlo stochastic optimization scheme such as \cite{montecarlo} is that we have a strong suspicion that our true objective function is locally pretty smooth, which fits nicely with local search based methods like PSO.
 Additionally using more particles helps us avoid local minima to which genetic algorithms are susceptible as suggested by \cite{geneticalgorithm}.
@@
      \STATE Pick random numbers $r_p, r_g \sim U(0,1)$.
-     \STATE Set $v_i = \omega v_i + \omega_p r_p (p_i - x_i) + \omega_g r_g (p -x_i)$.
+     \STATE Set $v_i = \omega v_i + \phi_p r_p (p_i - x_i) + \phi_g r_g (p -x_i)$.
      \STATE Set $x_i = x_i + v_i$.
@@
 \subsection{Performance and Results}
+Overall, we found that on the standard capture map, agents whose weights were selected by PSO tended to perform slightly worse than our hand-optimized agent, tying 61.5\% of the time, losing 30.7\% of the time, and only winning 7.7\% of the time.
+In determining the reason for this apparent failure of PSO, we determined that for an average variable optimized by PSO, across all different maps we attempted, the standard deviation was 29.8\% of the possible range, and 39.8\% of the observed range.
+In other words, PSO returned very different optimized results for different layouts.
+Indeed, PSO won 38.5\% of the time, tied 46.1\% of the time, and lost 15.4\% of the time on the map for which it had been optimized.
 
@@
 To solve this problem of disparate weights selected by PSO for different layouts, given a layout, we attempted to determine similar layouts for which we had already computed training data.
-The idea was that using the single ``closest'' layout would be a mistake since each of our weights were computed by PSO and were thus subject to noise; adding independent results therefore seems likely to result in better performance.
+The idea was that using the single ``closest'' layout would be a mistake since each of our weights were computed by PSO and were thus subject to noise; averaging independent results therefore seems likely to result in better performance.
 
@@
 Additionally we extracted some features from each board - such as amount of food, size and number of agents.
-Then we used k-means clustering to choose a handful of clusters that capture the data pretty well.
-The choice of k-means clustering was done because it seemed likely that clustering might help as suggested by \cite{textbook} and we consider k-means clustering to be the default for problems without a prior \cite{kmeans}.
-Moreover the the centroid of a set of points is the natural choice for how we would mix a set of heuristics, making k-means seem to match the same prior.
+Then we used $k$-means clustering to choose a cluster similar to our observed layout.
+We chose $k$-means as clustering can stabilize disparate data \cite{textbook} and we consider $k$-means the default for problems without a prior \cite{kmeans}.
+Moreover the the centroid of a set of points is the natural choice for how we would mix a set of heuristics, and $k$-means matches the same metric.
 
@@
 \subsection{Performance and Results}
+Overall, clustering significantly improved the efficacy of our PSO-optimized weights.
+In comparison to our hand-optimized agent, among games that one of the two agents won, our averaged PSO-weighted agent won approximately 64\% of the games.
+The data suggests that clustering was able to mitigate the damage of optimizing to the wrong board, and allow us to better approximate an optimal weighting.
 
 \section{Discussion}
+Our approach to Pac-Man consisted of a mix of human-determined approaches and machine learning.
+We began with a collection of agents that were primarily human-optimzied, using pre-determined weights on a subset of the heuristics described above for evaluation on a Minimax tree.
+These agents was only marginally more successful than the reflex agents, and had several key shortcomings; namely, that they were unable to coordinate -- to choose offense or defense -- and lacked optimal parameters.
+We solved the first problem initially by assigning weights to a series of board meta-analysis conditions to switch between agent recommendations.
+This substantially improved the robustness of our player, but our hand-optimized weights were still quite weak.
+Our inital approach to use binary Particle Swarm Optimization to optimize these parameters was ineffective in practice, because PSO tended to give heavily board-specific weights with high variance between boards.
+Applying $k$-means clustering was effective in concert with PSO to ensure that the weights suggested by our particle swarm were effectively applied to a given layout.
+
+Overall, our agent's strongest asset is its flexibility -- a result of a wide variety of heuristics generated from human analysis of the game, PSO to develop correct weightings across different maps, and clustering to determine the proper gametime weighting.
+Continued improvement could be achieved by using standard PSO, rather than binary PSO, assuming we had some objective function to minimize.
+Such a function would likely be an objective measure of percentage success against a static cross-section of agents, such as repeated participation in a nightly tournament.
+Additionally, running PSO and $k$-means on a larger set of layouts would likely give our agent more flexibility and encourage better performance on nonstandard layouts.
 
@@
 
+\bibitem{pars} Parsopoulos, K.
+E., Vrahatis, M.
+N.
+(2001) Particle Swarm Optimizer in Noisy and Continuously Changing Environments.
+{\it Proceeding of the IASTED International Conference on Artificial Intelligence and Soft Computing} (ASC 2001), Cancun, Mexico.
+pp.
+289-294.
+
 \bibitem{geneticalgorithm} Rocha, M., Neves J.

### 2011-03-09 contest/ourAgent.py

@@ -165,8 +165,6 @@ class ourAgent(CaptureAgent,minimaxModule.MinimaxModuleDelegate, ParticleSwarmOp
     self.inferenceModule.initialize(gameState, self.isRed, self.enemies, self.index)#infModule checks to make sure we don't do this twice
     self.cellLayout = cellLayout.CellLayout(gameState.data.layout, self.distancer) # pass one of these guys around
     
-    curAgent.setWeights(weightsConfig.WeightsMap)
-    
     self.holdTheLineModule = holdTheLineModule.holdTheLineModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
     self.defenseModule = defenseModule.defenseModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
     self.attackModule = attackModule.AttackModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)

### 2011-03-09 contest/particleSwarmOptimizer.py

@@ -66,8 +66,7 @@ class Particle:
                 self.position[key] = max
             if(self.position[key] < min):
                 self.position[key] = min
-    
-    
+                
         
         
         
@@ -84,7 +83,7 @@ class ParticleSwarm:
         self.bestKnown = potentialBests[0].bestKnown.copy()
         if(len(potentialBests) > 1):
             print "Tie in init, so set up default player as best"
-            self.bestKnownVal += 1 # tiebreak, for swarm consistency
+            self.bestKnownVal += 100 # tiebreak, for swarm consistency
             potentialBests[0].bestKnown = optimizableDelegate.getDefaultWeights().copy()
             potentialBests[0].bestKnownVal = self.bestKnownVal
             self.bestKnown = potentialBests[0].bestKnown.copy()
@@ -112,7 +111,10 @@ class ParticleSwarmOptimizer:
       if(self.verbose):
           print("STARTING OPTIMIZE!")
       for i in range(numIterations):
+          curCount = 0
           for particle in self.swarm.particles:
+              curCount += 1
+              if(self.verbose): print("Currently on particle " + str(curCount) +"/" + str(len(self.swarm.particles)) + " in round " + str(i+1) + "/" + str(numIterations))
               particle.updateVelocity()
               particle.updatePosition()
               particleVal = self.fitnessFunction(self, particle)
@@ -214,7 +216,7 @@ class ParticleSwarmOptimizer:
       if(games[0].state.data.score > 0): #Red wins
           return particle.swarm.bestKnownVal
           
-      return particle.swarm.bestKnownVal + 1
+      return particle.swarm.bestKnownVal + 20
       
           
 if __name__ == '__main__':

### 2011-03-09 projectWriteup/paper.tex

@@
 \section{Introduction}
-A popular and relevant field in artificial intelligence is noisy gameplay
-\cite{miik}.  One fun example of this field is Capture the Flag (CTF)
+A popular and relevant field in artificial intelligence is noisy gameplay\cite{miik}.  One fun example of this field is Capture the Flag (CTF)
 Pac-Man.  In this paper, we discuss our implementation of an optimized, flexible agent to play CTF Pac-Man.
@@
 However, because we were able to deduce an exact location any time food went missing, any agent that was doing serious harm was inherently easy to track.
+
 \subsection{Hold the Line}

### 2011-03-09 contest/ourAgent.py
Relied on mixed weights

@@ -1,3 +1,5 @@
+import boardExtractor
+import kMeansClassifier
 from captureAgents import AgentFactory
 from captureAgents import CaptureAgent
 import distanceCalculator
@@ -164,8 +166,32 @@ class ourAgent(CaptureAgent,minimaxModule.MinimaxModuleDelegate, ParticleSwarmOp
 
     self.inferenceModule.initialize(gameState, self.isRed, self.enemies, self.index)#infModule checks to make sure we don't do this twice
     self.cellLayout = cellLayout.CellLayout(gameState.data.layout, self.distancer) # pass one of these guys around
+    thisLayoutInfo = boardExtractor.vectorize(gameState.data.layout,self.cellLayout)
+    boardValues = knownWeights.ClusteringValues
+    boardValues['thisone'] = thisLayoutInfo
+   
+    clusters, clusterElements =kMeansClassifier.kMeans(boardValues,4)
     
-    curAgent.setWeights(weightsConfig.WeightsMap)
+    ourCluster =None
+    for cluster in clusterElements:
+      if 'thisone' in clusterElements[cluster]:
+        ourCluster =cluster
+    
+    cellmates = list(clusterElements[ourCluster])
+    cellmates.remove('thisone')
+
+    playingWeights = util.Counter()
+    for mate in cellmates:
+      for key in knownWeights.WeightsMap[mate]:
+        playingWeights[key] += knownWeights.WeightsMap[mate][key]
+    
+    playingWeights.divideAll(float(len(cellmates)))
+ 
+    #print playingWeights
+      
+
+#    self.setWeights(playingWeights)
+    self.setWeights(weightsConfig.WeightsMap)
     
     self.holdTheLineModule = holdTheLineModule.holdTheLineModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)
     self.defenseModule = defenseModule.defenseModule( self.friends, self.enemies, self.isRed,self.index, self.heuristicWeights, self.inferenceModule, self.cellLayout, self.distancer)

### 2011-03-09 projectWriteup/paper.tex

--- 2011-03-09 projectWriteup/paper.tex
@@
 \section{Introduction}
-A popular and relevant field in artificial intelligence is noisy gameplay
-\cite{miik}.  One fun example of this field is Capture the Flag (CTF)
+A popular and relevant field in artificial intelligence is noisy gameplay \cite{miik}.  One fun example of this field is Capture the Flag (CTF)
 Pac-Man.  In this paper, we discuss our implementation of an optimized, flexible agent to play CTF Pac-Man.
@@
 We thought much more about our choice of heuristics than about their weights, relying instead on automated techniques to choose optimal parameters.
-Our choice of heuristics was primarily driven by attempting to think about things in ways similar to humans; in each ``mode" we evaluated the position using heuristics relevant to examining the board from the perspective of the human strategy.
+Our choice of heuristics was primarily driven by attempting to think about things in ways similar to humans; in each ``mode'' -- offense, defense, and hold the line -- we evaluated the positions using heuristics relevant to examining the board from the perspective of the human strategy.
 
@@
 Our agents mirror their moves, trying to stay closer to all of the squares on the border than the opponents that that agent was ``covering''.
-With good inference, as is possible in a 6 agent game, it could become very hard for any opposing agents to cross the border.
+With good inference, as is possible in a six-agent game, it could become very hard for any opposing agents to cross the border.
 

### 2011-03-09 contest/knownWeights.py
PSO Weights in

@@ -3,26 +3,26 @@
 LayoutMap = {}
 
 
-WeightsMap = { "contest01Capture":{'hltAgent_opponentMax': 3.1463242810722329, 'attackModule_nearestCapsuleCoeff': -10, 'defenseModule_avgAvgDistances': 100, 'attackModule_distanceApartReward': 10, 'attackModule_nearestFoodPower': 1, 'attackModule_totalFoodCoeff': 10, 'defenseModule_maxMinOrZero': 18.551861681679497, 'ourAgent_attackWeight': 0.78792355981096796, 'ourAgent_hltWeight': 1, 'hltAgent_zerosecondMax': -0.32425376337136047, 'attackModule_distanceToEnemies': 10, 'attackModule_foodEatenReward': 4000, 'defenseModule_safeFood': -100, 'hltAgent_lackHLT': -100, 'hltAgent_secondMax': 4.9029622676815841, 'attackModule_trappedPenaltyCoeff': 84.071715300586462, 'attackModule_nearestFoodCoeff': -8.5453120029128922, 'defenseModule_averageThreat': 100, 'ourAgent_theyCanBeAttackingThreshold': 17.265760885966358, 'defenseModule_avgMin': -100, 'hltAgent_ourMaxDistance': 5, 'ourAgent_canBeAttackingThreshold': 16.05314865392722, 'hltAgent_teamavgMinDistanceToEdge': -4.0674648764491224, 'defenseModule_lackDefenders': 21.868317709300729, 'hltAgent_averageInactivity': -10, 'hltAgent_ourAverageDistanceToSquares': 5, 'ourAgent_dWeight': 0.53126065984164217, 'defenseModule_maxMin': -100, 'attackModule_percentImpatience': 96.873730871912556}, \
[…]

### 2011-03-09 contest/baselineAgents.py
A final commit.

@@ -23,10 +23,9 @@ NUM_KEYBOARD_AGENTS = 0
 class BaselineAgents(AgentFactory):
   "Returns one keyboard agent and offensive reflex agents"
 
-  def __init__(self, isRed, first='offense', second='offense', rest='offense'):
+  def __init__(self, isRed, first='offense', second='defense', rest='offense'):
     AgentFactory.__init__(self, isRed)
-    #self.agents = [first, second]
-    self.agents = ['offense', 'keys']
+    self.agents = [first, second]
     self.rest = rest
 
   def getAgent(self, index):
@@ -96,7 +95,6 @@ class ReflexCaptureAgent(CaptureAgent):
 
     maxValue = max(values)
     bestActions = [a for a, v in zip(actions, values) if v == maxValue]
-#    print 'bestactions: ' + str(bestActions) + ' achieve value ' + str(maxValue)
 
     return random.choice(bestActions)
 

### 2011-03-09 contest/boardExtractor.py

@@ -1,0 +1,2 @@
+def vectorize(layout, cellLayout):
+  return [layout.width, layout.height, len(layout.walls.asList(True)), len(layout.food.asList(True)), len(layout.capsules), len(cellLayout.cells)]

### 2011-03-09 contest/capture.py

@@ -299,10 +299,11 @@ class GameState:
       return configOrPos.pos[0] < width / 2
 
 def halfGrid(grid, red):
-  halfway = grid.width / 2
+  tilewidth = grid.width - 1
+  halfway = tilewidth / 2
   halfgrid = Grid(grid.width, grid.height, False)
   if red:    xrange = range(halfway)
-  else:       xrange = range(halfway, grid.width)
+  else:       xrange = range(halfway, tilewidth)
 
   for y in range(grid.height):
     for x in xrange:
@@ -583,9 +584,9 @@ def readCommand( argv ):
   parser = OptionParser(usageStr)
 
   parser.add_option('-r', '--red', help=default('Red team'),
-                    default='')
+                    default='BaselineAgents')
   parser.add_option('-b', '--blue', help=default('Blue team'),
-                    default='')
+                    default='BaselineAgents')
   parser.add_option('--redOpts', help=default('Options for red team (e.g. first=keys)'),
                     default='')
   parser.add_option('--blueOpts', help=default('Options for blue team (e.g. first=keys)'),
@@ -602,16 +603,13 @@ def readCommand( argv ):
   parser.add_option('-Q', '--super-quiet', action='store_true', dest="super_quiet",
                     help='Same as -q but agent output is also suppressed', default=False)
 
-  parser.add_option('-v', '--verbose', action='store_true', dest="verbose",
-                    help='Include our debug info', default=False)
-
   parser.add_option('-k', '--numPlayers', type='int', dest='numPlayers',
                     help=default('The maximum number of players'), default=4)
   parser.add_option('-z', '--zoom', type='float', dest='zoom',
                     help=default('Zoom in the graphics'), default=1)
   parser.add_option('-i', '--time', type='int', dest='time',
                     help=default('TIME limit of a game in moves'), default=3000, metavar='TIME')
-  parser.add_option('-n', '--numGames', type='int', dest='numGames',
+  parser.add_option('-n', '--numGames', type='int',
                     help=default('Number of games to play'), default=1)
   parser.add_option('-f', '--fixRandomSeed', action='store_true',
                     help='Fixes the random seed to always play the same game', default=False)
@@ -646,9 +644,6 @@ def readCommand( argv ):
     import graphicsDisplay
[…]

### 2011-03-09 contest/captureAgents.py

@@ -91,10 +91,9 @@ class CaptureAgent(Agent):
     self.distancer.getDistance(p1, p2)
     """
     self.red = gameState.isOnRedTeam(self.index)
-    self.distancer = distanceCalculator.Distancer(gameState.data.layout)
-    
+    self.distancer = distanceCalculator.Distancer(gameState.data.layout) 
     # comment this out to forgo maze distance computation and use manhattan distances
-    self.distancer.getMazeDistances()
+    #:self.distancer.getMazeDistances()
     
     import __main__
     if '_display' in dir(__main__):

### 2011-03-09 contest/ourAgent.py

@@ -54,7 +54,6 @@ class inferenceModule():
 
     self.distancer = distanceCalculator.Distancer(layout)
     self.distancer.getMazeDistances()
-
     self.ourSideDistancer = distanceCalculator.Distancer(ourSideLayout)
     self.ourSideDistancer.getMazeDistances()
 
@@ -157,6 +156,7 @@ class ourAgent(CaptureAgent,minimaxModule.MinimaxModuleDelegate, ParticleSwarmOp
 
   def registerInitialState(self, gameState):
     CaptureAgent.registerInitialState(self,gameState)
+    self.distancer.getMazeDistances()
     if self.isRed:
       self.friends = gameState.getRedTeamIndices()
       self.enemies = gameState.getBlueTeamIndices()

### 2011-03-09 contest/teams/DangerZone/attackModule.py
Preparing to commit

@@ -1,0 +1,171 @@
+import module
+from module import agentModule
+import minimaxModule
+from minimaxModule import MinimaxModule
+import random
+import time
+import cellLayout
+
+class AttackModule(agentModule, minimaxModule.MinimaxModuleDelegate):
+
+  def chooseAction(self, gameState):
+      print("Agent " + str(self.index) + " choosing an action")
+      minimaxMod = MinimaxModule(self)
+      minimaxMod.setImpatience(float(self.heuristicWeights['attackModule_percentImpatience'])/100.0)
+      minimaxVals = minimaxMod.getMinimaxValues(gameState, self.index, self.isRed, 0.1)
+      bestActions = []
+      bestVal = 0
+      for pair in minimaxVals:
+          if(bestVal < pair[1]):
+              bestActions = []
+          if(len(bestActions) == 0 or (bestVal == pair[1])):
+              bestActions.append(pair[0])
+              bestVal = pair[1]
+      
+      if(len(bestActions) == 0):
+          return gameState.getLegalActions(self.index)[0]
+      return random.choice(bestActions)
+
+  def getStateValue(self, gameState):
+      foodDistances = self.distanceToFood(gameState, not self.isRed)
+      nearestFoodVal = self.heuristicWeights['attackModule_nearestFoodCoeff'] * pow(foodDistances[0], self.heuristicWeights['attackModule_nearestFoodPower'])
+      totalFoodVal = self.heuristicWeights['attackModule_totalFoodCoeff'] * foodDistances[1]
+      nearestCapsuleVal = self.heuristicWeights['attackModule_nearestCapsuleCoeff'] * self.nearestCapsule(gameState)
+      foodCount = self.getFoodCount(gameState, not self.isRed)
+      numFoodsVal = self.heuristicWeights['attackModule_foodEatenReward'] * self.getFoodCount(gameState, not self.isRed)
+      distanceApartVal = self.heuristicWeights['attackModule_distanceApartReward'] * self.distanceApart(gameState)
+      enemyDistanceVal = self.heuristicWeights['attackModule_distanceToEnemies'] * self.distanceToEnemies(gameState)
+      trappedPenaltyVal = self.heuristicWeights['attackModule_trappedPenaltyCoeff'] *self.trappedPenalty(gameState)
+      return -numFoodsVal - nearestFoodVal - totalFoodVal - nearestCapsuleVal + distanceApartVal + enemyDistanceVal + trappedPenaltyVal
[…]

### 2011-03-09 contest/teams/DangerZone/cellLayout.py

@@ -1,0 +1,256 @@
+import game
+from game import Grid
+
+DEBUG = True
+PRINTDEBUG = False
+
+class LayoutNode:
+    def __init__(self, pos):
+        self.positions = [pos]
+        self.neighbors = []
+    
+    def __hash__(self):
+        if(len(self.positions) == 0): return 0
+        return hash(self.positions[0]) #since each graph will have a position in only one node this should work
+        
+    def __len__(self):
+        if(self.positions == None):
+            return 0
+        return len(self.positions)
+    
+    def __str__(self):
+        return str(self.positions)
+    
+    def getNeighbors(self):
+        return self.neighbors
+    
+    def getPositions(self):
+        return self.positions
+
+class CellLayout:
+    def __init__(self, layout, distancer):
+        self.distancer = distancer
+        self.layout = layout
+        self.walls = layout.walls
+        onBoardPos = self.getLegalPosition()
+        initialNode = LayoutNode(onBoardPos)
+        self.cells = {onBoardPos: initialNode}
+        self.expandGrid(initialNode)
+        if(DEBUG):
+            self.debugCheck()
+        pivotNode = self.getBestNeighbor()
+        if(PRINTDEBUG):
+            print pivotNode.getPositions()
+            for neighbor in pivotNode.getNeighbors():
+                print neighbor.getPositions()
+        # use the pivot node to contract the grid, since we can assume
+        # it is either a singleton node (splitter or crossroads), in
+        # which case it works like a champ or it is a double or single,
+        # in which case the board is so simple it shouldn't matter anyway
+        self.contractGrid(pivotNode)
+        if(DEBUG):
+            self.debugCheck()
+        if(PRINTDEBUG):
+            for cell in set(self.cells.values()):
+                print cell
+        
+        
+    # should only be ever called at the beginning, before
+    # contracting.  It assumes that each node has only one
+    # position.    
+    def expandGrid(self, startNode):
+        curPos = startNode.getPositions()[0]
+        possiblePositions = [(curPos[0] + 1, curPos[1]), (curPos[0] - 1, curPos[1]), (curPos[0], curPos[1] + 1), (curPos[0], curPos[1]-1)]
+        expandPositions = [pos for pos in possiblePositions if (0 <= pos[0] and pos[0] < self.walls.width and 0 <= pos[1] and pos[1] < self.walls.height and not self.walls[pos[0]][pos[1]])]
+        if(PRINTDEBUG):
[…]

### 2011-03-09 contest/teams/DangerZone/defenseModule.py

@@ -1,0 +1,114 @@
+import capture
+import module
+def avg(list):
+  return float(sum(list)) / len(list)
+
+class defenseModule(module.agentModule):
+  def chooseAction(self, gameState, defensiveMatching,attackingEnemies):
+    actions = gameState.getLegalActions(self.index)
+
+    bestaction = None
+    bestranking = -1e10
+    besttiebreaker = -1e10
+    enemyPositions = self.inferenceModule.getEnemyMLEs().values()
+    for action in actions:
+      newState=gameState.generateSuccessor(self.index,action)
+      if not self.inferenceModule.isOnOurSide(self.whereAreWe(newState)):
+        continue
+      actionranking = self.evaluateBoard([newState.getAgentPosition(p) for p in defensiveMatching],self.getOurFood(newState), self.inferenceModule.getEnemyMLEs().values())
+      if actionranking>bestranking:
+        bestaction = action
+        bestranking = actionranking
+
+    #print "For best action " + str(bestaction) + " we do utility " + str(action)
+    return bestaction
+
+  def getSuccessor(self, gameState, action):
+    """
+    Finds the next successor which is a grid position (location tuple).
+    """
+    successor = gameState.generateSuccessor(self.index, action)
+    pos = successor.getAgentState(self.index).getPosition()
+    if pos != nearestPoint(pos):
+      # Only half a grid position was covered
+      return successor.generateSuccessor(self.index, action)
+    else:
+      return successor
+  
+  def getMinDistanceToEachSquare(self,ourpositions,squares,isUs):
+    distances = []
+    for border in squares:
+      if not isUs:
+      	distances.append(min([self.getMazeDistance(border,p) for p in ourpositions]))
+      else:
+        distances.append(min([self.getOurSideMazeDistance(border,p) for p in ourpositions]))
+    return distances
+
+  def getAvgDistanceToEachSquare(self,ourpositions,squares,isUs):
+    distances = []
+    for border in squares:
+      if not isUs:
+        distances.append(avg([self.getMazeDistance(border,p) for p in ourpositions]))
+      else:
+        distances.append(avg([self.getOurSideMazeDistance(border,p) for p in ourpositions]))
+    return distances
+
+  def getMaxDelta(self, ourD, theirD):
[…]

### 2011-03-09 contest/teams/DangerZone/holdTheLineModule.py

@@ -1,0 +1,142 @@
+import capture
+import module
+
+def secondMin(list):
+  try:
+    return sorted(list)[1]
+  except:
+    return 0
+
+class holdTheLineModule(module.agentModule):
+  def chooseAction(self, gameState, ourIndices,ourEnemies):
+    actions = gameState.getLegalActions(self.index)
+
+    bestaction = None
+    bestranking = -1e10
+    for action in actions:
+      newState=gameState.generateSuccessor(self.index,action)
+      if not self.inferenceModule.isOnOurSide(self.whereAreWe(newState)):
+        continue
+      actionranking = self.evaluateBoard(newState, ourIndices, ourEnemies)
+      if actionranking>bestranking:
+        bestaction = action
+        bestranking = actionranking
+
+    #print 'Our action ' + str(action) + ' our score ' + str(bestranking)
+    return bestaction
+
+  def getSuccessor(self, gameState, action):
+    """
+    Finds the next successor which is a grid position (location tuple).
+    """
+    successor = gameState.generateSuccessor(self.index, action)
+    pos = successor.getAgentState(self.index).getPosition()
+    if pos != nearestPoint(pos):
+      # Only half a grid position was covered
+      return successor.generateSuccessor(self.index, action)
+    else:
+      return successor
+  
+  def maxMinDistanceToSquares(self, ourpositions, squares):
+    currentworst = -1e10
+    for square in squares:
+      thissquarevalue = min([self.getOurSideMazeDistance(square,p) for p in ourpositions])
+      if thissquarevalue>currentworst:
+        currentworst =thissquarevalue 
+    return currentworst
+ 
+  def getMinDistanceToSquares(self,agentPositions, squares,isUs):
+    distances = []
+    for square in squares: 
+      if isUs:
+        distances.append(min([self.getOurSideMazeDistance(square,p) for p in agentPositions]))
+      else:
+        distances.append(min([self.getMazeDistance(square,p) for p in agentPositions]))
+    return distances
+  
+  def getSecondMinDistanceToSquares(self,agentPositions, squares,isUs):
+    distances = []
+    for square in squares:
+      if isUs:
+        distances.append(secondMin([self.getOurSideMazeDistance(square,p) for p in agentPositions]))
+      else:
[…]

### 2011-03-09 contest/teams/DangerZone/knownWeights.py

@@ -1,0 +1,51 @@
+# knownWeights.py
+
+LayoutMap = {}
+
+
+WeightsMap = { "contest01Capture":{'hltAgent_opponentMax': -10, 'attackModule_nearestCapsuleCoeff': 9.6081461876909948, 'defenseModule_avgAvgDistances': -100, 'attackModule_distanceApartReward': -3.3981353624296373, 'attackModule_nearestFoodPower': 2, 'attackModule_totalFoodCoeff': 10, 'defenseModule_maxMinOrZero': 31.256439569054052, 'ourAgent_attackWeight': 0, 'ourAgent_hltWeight': 0.41195719055357016, 'hltAgent_zerosecondMax': 1.8387304650231648, 'attackModule_distanceToEnemies': 10, 'attackModule_foodEatenReward': 4000, 'defenseModule_safeFood': 100, 'hltAgent_lackHLT': -16.18569330754012, 'hltAgent_secondMax': -10, 'attackModule_trappedPenaltyCoeff': 100, 'attackModule_nearestFoodCoeff': 7.861508272243884, 'defenseModule_averageThreat': 34.559757054373819, 'ourAgent_theyCanBeAttackingThreshold': 19.417025085729261, 'defenseModule_avgMin': -4.5581753683551511, 'hltAgent_ourMaxDistance': -10, 'ourAgent_canBeAttackingThreshold': 14.302651451282919, 'hltAgent_teamavgMinDistanceToEdge': 5, 'defenseModule_lackDefenders': -50, 'hltAgent_averageInactivity': -15, 'hltAgent_ourAverageDistanceToSquares': 5, 'ourAgent_dWeight': 0.12337859591612532, 'defenseModule_maxMin': 100, 'attackModule_percentImpatience': 87.729658188970873} ,\
[…]

### 2011-03-09 contest/teams/DangerZone/minimaxModule.py

@@ -1,0 +1,135 @@
+import capture
+import game
+import time
+from util import Queue
+
+DETECT_CYCLES = True
+PRINTDEBUG = False
+
+class MinimaxModuleDelegate:
+    
+  def getStateValue(self, gameState):
+      return 0
+
+"""
+A self-expanding node for a minimax tree
+"""
+class MinimaxNode:
+  def __init__(self, parent, gameState, agentIndex, delegate, ignoreIndices, action = None):
+      self.parent = parent
+      self.state = gameState
+      self.index = agentIndex
+      self.delegate = delegate
+      self.action = action
+      self.ignoreIndices = ignoreIndices
+      self.value = self.delegate.getStateValue(gameState)
+      self.children = []
+      
+  def expand(self):
+      if(len(self.children) == 0): #only expand if we haven't already
+          if(DETECT_CYCLES):
+              curNode = self.parent
+              cycle = False
+              for i in range(2 * self.state.getNumAgents()):
+                  if(not DETECT_CYCLES or curNode == None):
+                      break
+                  curNode = curNode.parent
+              if(curNode != None):
+                  redIndex = (self.index in self.state.getRedTeamIndices())
+                  curNodeFood = curNode.state.getBlueFood() if redIndex else curNode.state.getRedFood()
+                  selfNodeFood = self.state.getBlueFood() if redIndex else curNode.state.getRedFood()
+                  if(curNode.state.getAgentPosition(self.index) == self.state.getAgentPosition(self.index) and curNodeFood == selfNodeFood):
+                      cycle = True
+          if(not (DETECT_CYCLES and cycle)): # don't expand cyclic graphs
+              numAgents = self.state.getNumAgents()
+              nextIndex = (self.index + 1) % numAgents
+              while(nextIndex in self.ignoreIndices):
+                  if(nextIndex == self.index): break # avoid infinite loops
+                  nextIndex = (nextIndex + 1) % numAgents
+              if(self.state.getAgentPosition(self.index) == None): #if we don't know how to expand the state at the given 
+                  self.children.append(MinimaxNode(self, self.state, nextIndex, self.delegate, self.ignoreIndices, None))
+              else:
+                  actions = self.state.getLegalActions(self.index)
+                  for action in actions:
+                      nextState = self.getSuccessor(self.state, action)
[…]

### 2011-03-09 contest/teams/DangerZone/module.py

@@ -1,0 +1,30 @@
+class agentModule():
+  def __init__(self, friends, enemies, isRed, index, heuristicWeights, inferenceModule, cellLayout, distancer=None):
+    self.friends=friends
+    self.enemies=enemies
+    self.isRed=isRed
+    self.index=index
+    self.heuristicWeights = heuristicWeights
+    self.distancer = distancer
+    self.inferenceModule = inferenceModule
+    self.cellLayout = cellLayout
+
+  def getOurFood(self,gameState):
+    if self.isRed:
+      return gameState.getRedFood().asList(True)
+    return gameState.getBlueFood().asList(True)
+
+  def whereAreWe(self, gameState):
+    return gameState.getAgentState(self.index).getPosition()
+
+  def getOurSideMazeDistance(self, posa, posb):
+    return self.inferenceModule.ourSideDistancer.getDistance(posa,posb)
+
+  def getMazeDistance(self,posa,posb):
+    return self.distancer.getDistance(posa,posb)
+ 
+  def getWhoMovedLast(self, gameState): #this is buggy since we might be first to move.    
+    return (self.index-1) % (len(self.friends) + len(self.enemies))
+
+  def chooseAction(self,gameState):
+    return gameState.getLegalActions(self.index)[0]

### 2011-03-09 contest/teams/DangerZone/opponentModeler.py

@@ -1,0 +1,87 @@
+import capture
+from capture import GameState
+from game import GameStateData
+from game import Configuration
+from game import Directions
+import ourAgent
+import util
+import random
+
+class opponentModel():
+  def __init__(self,inferenceModel):
+    self.iModel = inferenceModel
+  
+  def updatePositionsBasedOnSensor(self, gameState, ourAgentPos):
+    agentdistances = gameState.getAgentDistances()
+    ourAgentEaten = (ourAgentPos == gameState.getInitialAgentPosition(self.iModel.index))
+    for enemy in self.iModel.enemypositions: #this is iterating over the keys to a map
+      enemyPos = gameState.getAgentPosition(enemy)
+      if enemyPos:
+        self.iModel.enemypositions[enemy] = util.Counter()
+        self.iModel.enemypositions[enemy][gameState.getAgentPosition(enemy)] = 1
+	self.iModel.lastKnownDistances[enemy] = util.manhattanDistance(enemyPos, ourAgentPos)
+      else:
+        if (not ourAgentEaten and self.iModel.lastKnownDistances[enemy] <= capture.SIGHT_RANGE - 3): #enemy was eaten, otherwise they'd be observable
+          print "We think an enemy was eaten"
+  	  self.iModel.enemypositions[enemy] = util.Counter()
+          self.iModel.enemypositions[enemy][gameState.getInitialAgentPosition(enemy)] = 1
+          self.iModel.lastKnownDistances[enemy] = 99999
+        observeddistance = agentdistances[enemy]
+        for pos in self.iModel.enemypositions[enemy]:
+          if capture.SIGHT_RANGE < util.manhattanDistance(pos,ourAgentPos):
+            self.iModel.enemypositions[enemy][pos] = self.iModel.enemypositions[enemy][pos] * gameState.getDistanceProb(util.manhattanDistance(ourAgentPos,pos), observeddistance)
+          else:
+            self.iModel.enemypositions[enemy][pos] = 0
+#          self.enemypositions[enemy] = self.enemypositions[enemy] * gameState.getDistanceProb(1, observeddistance)
+      self.iModel.enemypositions[enemy].normalize()
+    
+  def updatePositionsBasedOnFood(self, agentIndex, gameState):
+    if(self.iModel.isRed):
+      newGrid = gameState.getRedFood()
+    else:
+      newGrid = gameState.getBlueFood()
+    for i in range(newGrid.width):
+      for j in range(newGrid.height):
[…]

### 2011-03-09 contest/teams/DangerZone/particleSwarmOptimizer.py

@@ -1,0 +1,252 @@
+import capture
+import game
+import random
+import sys
+
+PHI_P = 1
+PHI_G = 1
+OMEGA = 1
+
+class ParticleSwarmOptimizable:
+  
+  # Return a dictionary
+  def getDefaultWeights(self):
+      return {}
+  
+  def getWeightMin(self, weightName):
+      return -10
+  
+  def getWeightMax(self, weightName):
+      return 10
+  
+  def setWeights(self, weights):
+      self.weights = weights
+
+
+class Particle:
+    
+    def __init__(self, swarm):
+        self.swarm = swarm
+        self.optimizableDelegate = swarm.optimizableDelegate
+        self.position = self.getRandomPosition()
+        self.velocity = self.getRandomVelocity()
+        self.bestKnown = self.position.copy()
+        self.bestKnownVal = 0
+        
+    def getRandomPosition(self):
+        pos = {}
+        for key in self.optimizableDelegate.getDefaultWeights():
+            min = self.optimizableDelegate.getWeightMin(key)
+            max = self.optimizableDelegate.getWeightMax(key)
+            newVal = random.uniform(min, max)
+            pos[key] = newVal
+        return pos
+    
+    def getRandomVelocity(self):
+        vel = {}
+        for key in self.position:
+            min = self.optimizableDelegate.getWeightMin(key)
+            max = self.optimizableDelegate.getWeightMax(key)
+            speed = random.uniform(min - max, max - min)
+            vel[key] = speed
+        return vel
+        
+    def updateVelocity(self):
+        rp = random.random()
+        rg = random.random()
+        for key in self.velocity:
+            self.velocity[key] = OMEGA * self.velocity[key] + PHI_P * rp * (self.bestKnown[key] - self.position[key]) + PHI_G * rg * (self.swarm.bestKnown[key] - self.position[key])
+            
+    def updatePosition(self):
+        for key in self.position:
+            min = self.optimizableDelegate.getWeightMin(key)
+            max = self.optimizableDelegate.getWeightMax(key)
+            self.position[key] = self.position[key] + self.velocity[key]
+            if(self.position[key] > max):
+                self.position[key] = max
+            if(self.position[key] < min):
+                self.position[key] = min
+                
+        
+        
+        
+class ParticleSwarm:
+    
+    def __init__(self, optimizableDelegate, numParticles, initFunction):
+        self.optimizableDelegate = optimizableDelegate
[…]

### 2011-03-09 contest/teams/DangerZone/weightsConfig.py

@@ -1,0 +1,86 @@
+# weightsConfig.py
+
+"""
+-----------------------
+  Weight Configuration
+-----------------------
+
+This file contains a dictionary used to weight modules, so they can presumably be
+machine optimized.
+
+"""
+
+# Map of weights we plan to use to determine a policy
+
+WeightsMap = { \
+                'attackModule_foodEatenReward' : 4000, \
+                'attackModule_nearestFoodPower' : 1, \
+                'attackModule_nearestFoodCoeff' : 20,  \
+                'attackModule_nearestCapsuleCoeff' : 1,  \
+                'attackModule_totalFoodCoeff'      : 2,  \
+                'attackModule_distanceApartReward' : 2,  \
+                'attackModule_distanceToEnemies'   : 10,  \
+                'attackModule_trappedPenaltyCoeff'   : 15,  \
+                'attackModule_percentImpatience'    : 10, \
+
+                'defenseModule_maxMinOrZero' : -10, \
+                'defenseModule_maxMin' : -5, \
+                'defenseModule_avgMin' : -5, \
+                'defenseModule_avgAvgDistances' : -.3, \
+                'defenseModule_averageThreat' : -13, \
+                'defenseModule_safeFood' : 3,\
+                'defenseModule_lackDefenders':-3, \
+
+                'ourAgent_hltWeight': .5, \
+                'ourAgent_dWeight' : .5, \
+                'ourAgent_attackWeight' : .01, \
+                'ourAgent_canBeAttackingThreshold' : 5, \
+                'ourAgent_theyCanBeAttackingThreshold' : 5, \
+
+                'hltAgent_ourAverageDistanceToSquares' : -2, \
+                'hltAgent_averageInactivity' : -10, \
+                'hltAgent_opponentMax' : -5, \
+                'hltAgent_secondMax' : -2, \
+                'hltAgent_zerosecondMax' : -2, \
+                'hltAgent_ourMaxDistance' : -1, \
+                'hltAgent_teamavgMinDistanceToEdge' : -2, \
+                'hltAgent_lackHLT' : -3, \
+              }
+
+# Map to specify the range that our weights can be in (bound as closely
+# as you can for values that will vary widely, such as exponents)
+
+WeightsRangeMap = { \
+                    'attackModule_foodEatenReward'     : (-1000, 4000), \
+                    'attackModule_nearestFoodPower'    : (1, 2),  \
[…]
